KO & EGGNOG

### 2019-11-27 scripts/05_pathway_feature_cpm.Rmd
update

```{r}
fn <- read_tsv('../data/humann2_res/humann2_final_out_cpm/humann2_pathabundance_cpm_unstratified.tsv') %>%
  rename(pathway = names(.)[1]) %>% 
  # remove the things up till the colon
  mutate(pathway = str_replace_all(pathway, '^.+\\: ','')) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # removing things in the parenthesis and remove the spaces in the pathway
  mutate(pathway = str_replace_all(pathway, ' \\(.+\\)',''),
         pathway = str_replace_all(pathway, ' ',''))
```

```{r}
# loading the enriched pathways from 6 combi and filter on the abundance matrix
feat_pw <- read_csv('../data/unique_enriched_pathways.csv')

cpms <- fn %>% 
  filter(pathway %in% feat_pw$pathway)

# only half is exactly the same

same_pw <- cpms %>% 
  pull(pathway)
```

```{r}
# plot the counts 
# get the pheno info of those samples
pheno <- read_csv('../data/current_pheno.csv')

res <- cpms %>% 
  gather(key = 'Sampleid', value = 'cpm', '1191V' : 'V0040A') %>% 
  left_join(pheno, by = 'Sampleid')

res
```

```{r}

same_pw %>% 
  map(~ res %>% 
          arrange(CR, desc(cpm)) %>% 
          filter(pathway == .) %>% 
          ggbarplot(x = 'Sampleid', y = 'cpm', fill = 'CR', color = 'CR') +
          scale_color_manual(values = c('#00468B', '#EC0000'))  +
          scale_fill_manual(values = c('#00468B', '#EC0000')) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
          labs(title = str_glue('Pathway: {.}')) +
          ggsave(str_glue('../figs/pathway_abundance_cpm_{.}.jpg'), width = 4, height = 3, dpi = 300))

for (i in same_pw) {
  res %>% 
          arrange(Toxicity, desc(cpm)) %>% 
          filter(pathway == i) %>% 
          ggbarplot(x = 'Sampleid', y = 'cpm', fill = 'Toxicity', color = 'Toxicity') +
          scale_color_manual(values = c('#00468B', '#EC0000'))  +
          scale_fill_manual(values = c('#00468B', '#EC0000')) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
          labs(title = str_glue('Pathway: {i}')) +
          ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/pathway_abundance_cpm/Toxicity/pathway_abundance_cpm_{i}.jpg'), width = 8, height = 6, dpi = 300)
}

```

```{r}
res %>% 
    arrange(CR, desc(cpm)) %>% 
    filter(pathway == 'pantothenateandcoenzymeAbiosynthesisI') %>% 
    ggbarplot(x = 'Sampleid', y = 'cpm', fill = 'CR', color = 'CR') +
    scale_color_manual(values = c('#00468B', '#EC0000'))  +
    scale_fill_manual(values = c('#00468B', '#EC0000')) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
    labs(title = str_glue('Pathway: pantothenateandcoenzymeAbiosynthesisI')) +
    ggsave(str_glue('../figs/tox/pathway_abundance_cpm_pantothenateandcoenzymeAbiosynthesisI.jpg'), width = 4, height = 3, dpi = 300)
```

>>>>

```{r}
pwa <- read_tsv('../data/humann2_res/humann2_final_out/humann2_pathabundance_cpm_unstratified.tsv') %>%
  dplyr::rename(pw = names(.)[1]) %>% 
  rename_all(funs(str_replace(., '_Abundance$',''))) %>% 
  # create a new column just to be pwid 
  mutate(pwid = str_extract(pw, '^.+:')) %>% 
  mutate(pwid = str_replace(pwid, ':',''))

  # removing things in the parenthesis and remove the spaces in the pathway
  # mutate(pathway = str_replace_all(pathway, ' \\(.+\\)',''),
  #        pathway = str_replace_all(pathway, ' ',''))

pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  dplyr::select(sampleid = Sampleid, 
         Toxicity,
         CR)
```

```{r}
sig <- read_csv('../data/unique_sig_pathway.csv') %>% 
  # extract the pw id part
  mutate(pwid = str_extract(pathway, '^.+_PWY|^PWY.+\\d{3,4}'))  %>% 
  mutate(pwid = str_replace_all(pwid, '_', '-'))

pwa_sig <- pwa %>% 
  filter(pwid %in% sig$pwid) %>% 
  dplyr::select(-pwid) %>% 
  gather(key = 'sampleid', value = 'abun', names(.)[2]:names(.)[ncol(.)]) %>% 
  left_join(pheno, by  = 'sampleid')
```

```{r}
# bar plot to show the cpm in each sample for each sig pathway
pw_list <- pwa_sig %>% 
  distinct(pw) %>% 
  pull(pw)

# tox
for (p in pw_list) {
  pwa_sig %>% 
    arrange(Toxicity, desc(abun)) %>% 
        filter(pw == p) %>% 
        ggbarplot(x = 'sampleid', y = 'abun', fill = 'Toxicity', color = 'Toxicity') +
          scale_color_manual(values = c('#00468B', '#EC0000'))  +
          scale_fill_manual(values = c('#00468B', '#EC0000')) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
          labs(title = str_glue('Pathway: {p}')) +
          ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/pathway_abundance_cpm/Toxicity/pathway_abundance_cpm_{p}.jpg'), width = 12, height = 10, dpi = 300)
}
```

```{r}
# CR
for (p in pw_list) {
  pwa_sig %>% 
    arrange(CR, desc(abun)) %>% 
        filter(pw == p) %>% 
        ggbarplot(x = 'sampleid', y = 'abun', fill = 'CR', color = 'CR') +
          scale_color_manual(values = c('#00468B', '#EC0000'))  +
          scale_fill_manual(values = c('#00468B', '#EC0000')) +
          theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8)) +
          labs(title = str_glue('Pathway: {p}')) +
          ggsave(str_glue('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/humann2_shotgun/figs/pathway_abundance_cpm/CR/pathway_abundance_cpm_{p}.jpg'), width = 12, height = 10, dpi = 300)
}
```

### 2019-11-27 scripts/12_lefse_genefam_term_ggplot.Rmd
update

```{r}
# load the lefse res of tox
# the input : lefse res files
fns <- list.files('../data/humann2_res/', pattern = 'genefam_abundace_pheno__[CR|Toxicity].+res$', full.names = T)
fns_name <- list.files('../data/lefse_genefam/', pattern = 'genefam_abundace_pheno__[CR|Toxicity].+res$')

>>>>

```{r}
# load the lefse res of tox
# the input : lefse res files
fns <- c(list.files('../data/humann2_res/lefse_ko/', pattern = '*/*.res$', full.names = T),
         list.files('../data/humann2_res/lefse_ko/', pattern = '*/*.res$', full.names = T))
